Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2023-02-17 manuscript.Rmd
make link to preprint clearer

The materials for this article are available on [GitHub](https://github.com/aaronpeikert/bayes-prereg) [@zenodo-release].
This version was created from git commit ``r repro::current_hash(backend = "gert")``.
The manuscript is available as preprint [@no-preprint-yet] and will be submitted to [Philosophical Psychology](https://www.tandfonline.com/journals/cphp20).

>>>>

The materials for this article are available on [GitHub](https://github.com/aaronpeikert/bayes-prereg) [@zenodo-release].
This version was created from git commit ``r repro::current_hash(backend = "gert")``.
The manuscript is available as [preprint](https://www.doi.org/10.31234/osf.io/cs8wb) [@peikertWhyDoesPreregistration2023] and was submitted to [Philosophical Psychology](https://www.tandfonline.com/journals/cphp20).
